Git Learning Notes

### 2015-01-19 ch-moox/moox.tex
walked in to exchange opinions with Advr, and walking out with his on wox and moox

\subsection{Synthesis Review of Molybdenum Oxide}

@@

The reactants used in this study were listed in Table~\ref{tb:mosource}. All reactants were used as received without further processing.

\begin{table}[htb]
\centering
\caption{Reactants list of \ce{MoO3} growth}\label{tb:mosource}
\begin{tabular}{lcccr}
\toprule
Material & Stock No & LOT &Purity & Vendor\\
\midrule
\ce{NaOH}     & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
\ce{NaI}      & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
\ce{Na2CO3}    & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
\ce{Molybdenum}& 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
\bottomrule
\end{tabular}
\end{table}

Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}. To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then naturally left dry in a convection hood. Other alkali ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment. 
\begin{table}[htb]
\centering
\caption{Physical constants of reactants }\label{tb:mothermo}
\begin{tabular}{lccr}
\toprule
Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & Reference\\
\midrule
\ce{NaOH}        & 318 & 1388 & \cite{crc1977}  \\
\ce{NaI}        & 651 & 1300 & \cite{crc1977}    \\
\ce{KI}        & 681 & 1330 & \cite{crc1977}   \\
\ce{Na2CO3}        & 851 & Not determined & \cite{crc1977}    \\
\ce{Na2MoO4}        & 687 & Not available & \cite{crc1977}   \\
\ce{MoO3}    & 795 & 1155 & \cite{crc1977}   \\
\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
\bottomrule
\end{tabular}
\end{table}
In a typical synthesis run (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile. Non-catalytic growth shares the same procedure except the NaOH treatment.

@@

\subsection{Non-catalyst Growth}\label{sec:nonsi}

The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.\cite{Levin1959} Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}. It is worth mentioning that these parameters are selected and optimized from a wide range of combinations. When the influence of one parameter is studied, the others are fixed, following the standard practice in controlled experiments.
%growth parameter
\begin{table}[htb]
\centering
\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
\begin{tabular}{lcccr}
\toprule
&&&\multicolumn{2}{c}{Flow (sccm)} \\
\cmidrule(l){4-5}
 & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure (mTorr) & Ar & \ce{O2}  \\
\midrule
Typical values  & 800    & 200 & 10 & 10  \\
\bottomrule
\end{tabular}
\end{table}

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}. The usual length of Si substrate is 1 inch. When positioned at 7 inch, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.
% cvd layout
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}. The triangular labels $\blacktriangledown$ were measured points at ambient environment. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}

From previous works in our group,\cite{predeep2011} it was found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{in 020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates. This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm. It was also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease. This is not surprising when considering the 3D temperature field in chamber requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}. Using conditions in Table~\ref{tab:mooxsi} and 2 h growth, this study observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}. Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34 \mu$m.
% sem in (31210-31510) batches
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.4\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.4\textwidth]{mosemsi_b}}
\caption[Representative morphologies of \ce{MoO3} on Si]{Representative morphologies of \ce{MoO3} on Si: (a) low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
\label{fig:mosisem}
\end{figure}

@@

  \textsuperscript{\emph{a}} R chain mode;

@@

Previous study in our group has found that \ce{MoO3} deposition on ITO glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction. A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, \emph{etc}. Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth. A literature search indeed shows that there exists a Na-Mo-O phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice that\footnote{http://forum.wordreference.com/showthread.php?t=244497} the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.

@@

Based on this phase diagram, the physical constants of reactants in Table~\ref{tb:mothermo}, and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences. First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then NaOH reacts with incoming \ce{MoO3} according to Formula~\ref{eq:pd}. 
\begin{subequations}\label{eq:pd}
\begin{align}
\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4 + H2O(g)\\
Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
\end{align}
\end{subequations}
The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is located in temperature zone between 650 and 350 \si{\degreeCelsius}. The actual temperature distribution during growth is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate. It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4. Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling droplet. \ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}.\footnote{This ratio considerably exceeds that of the usual metal catalyst scenario. This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial droplet, the concentration of sodium in final products is extremely low.}    Based on this aforementioned analysis, the author propose a hypothesis:
%theorem environment

The reaction on NaOH-Si substrate follow the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.

In a typical 2 h growth, the \ce{MoO3} weight increase is about 20 mg, which is about $1.4\times 10^{-4}$ mol. This amount far exceeds the applied NaOH of $5\times 10^{-7}$ mol.\footnote{Sec.~\ref{sec:grow} on page.~\pageref{sec:grow}} To capture the early stage growth, the supply of \ce{MoO3} must be reduced in a controlled way. This can be accomplished by tuning two factors: oxygen flow rate and growth time. In this thesis, two series of controlled growth were used to probe the evolution of \ce{MoO3} deposition on NaOH-Si substrate. The first series regulated \ce{O2} flow at 0.1, 1, 3 and 10 sccm with fixed growth time of 15 min. The second series controls growth time at 15, 30, 60, and 90 min with fixed \ce{O2} flow of 10 sccm. Two series share one common growth of 10 sccm \ce{O2} for 15 min.

The oxygen regulated growths were characterized using SEM, EDX and Raman, as shown in Fig.~\ref{fig:ch4oxy}. When \ce{O2} flow $\leq 1$ sccm, the deposition show micron size plate growth (Fig.~\ref{fig:ch4oxy}a and d). As oxygen flow becomes higher, the deposition amount increases dramatically, with a morphology of 1D forked plate decorated by triangular shape particles.
% sem
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{MoO3_EDX_Raman}
\caption[Evolution of the early stage for catalyst-assisted \ce{MoO3} growth]{Evolution of the early stage for catalyst-assisted \ce{MoO3} growth: SEM images, micro-Raman spectra, and EDX spectra of the specimens grown for 15 min with different \ce{O2} flows of (a-c) 0.1 sccm, (d-f) 1 sccm, (g-i) 3 sccm, and (j-l) 10 sccm. }
\label{fig:ch4oxy}
\end{figure}

Micro-Raman scattering was used to probe the phase change during the oxygen regulated growth. The Raman spectra of sodium molybdates is featured with multiple strong peaks located between 800 and 1000 \si{cm^{-1}}, which we refer as high-frequency region hereafter. \ce{MoO3} phase shows two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibits four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase shows even more peaks in high-frequency region, with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the rest three growths (Fig.~\ref{fig:ch4oxy}e, h, and k). This observation supports the previous hypothesis about the reaction sequence on NaOH-Si substrate (Formula~\ref{eq:pd}). Element analysis performed on the Raman sites also confirm the presence of Na, Mo and O in particles growth, and only Mo and O in the plate growth (Fig.~\ref{fig:ch4oxy}c, f, i, and l). It is worth noting that the absence of Na signal in the forked \ce{MoO3} plate indicates the doping level would be lower than the detection limit of 0.01 wt.\% if the Na doping ever occurs. It should be pointed out the existence of \ce{Na2Mo3O10} phase is in doubt so far, and no Raman fingerprint is reported.\cite{Fomichev1992}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX}
\caption[SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts. }
\label{fig:ch4edx1}
\end{figure}

@@

\begin{enumerate}
\item When no Mo powder is used, NaOH still holds onto substrate with some locations exhibiting etching.
\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular droplet-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism. Using Mo coated substrate and subsequent NaOH treatment, similar droplets formation was repeated. No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
\item 1 min growth shows plates in high temperature end and irregular shapes in low temperature end.
\item 15 min growth shows \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane. This is presumably due to the growth direction mismatch between different plates. Morphology will also depend on local NaOH concentration. NaOH trace mark turns into connected plates at the original locations, showing the high concentration mediated the morphology evolution. The possible catalyst solid was sitting on the top of plate layer. Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt. Two kinds of belts found, tapering and non-tapering. The former one seems to have droplets mostly associated with sidewalls of the top part.
\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip. XRD pattern indicated the existence of \ce{Na_xMoO3} phase. And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one droplet located along the interface of two perpendicular belts, EDX confirmed high Na content.
\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of droplets, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increase to 10 $\mu$ m in prolonged growth.
\end{enumerate}

>>>>

\subsection{Review of Synthesis Methods of Molybdenum Oxide}

@@

The reactants used in this study were listed in Table~\ref{tb:mosource}. All reactants were used as received without further processing.
\begin{table}[htb]
\centering
\caption{Reactants list of \ce{MoO3} growth}\label{tb:mosource}
\begin{tabular}{lcccr}
\toprule
Material & Stock No & LOT &Purity & Vendor\\
\midrule
\ce{NaOH}     & S318-500 & 070241 & 99.8\% & Fisher Scientific \\
\ce{NaI}      & 11665 & K11W054 & 99.9\% &  Alfa Aesar \\
\ce{KI}        & 42857 & H06Z051 & 99.9\% &  Alfa Aesar \\
\ce{Na2CO3}    & 33377 & 114X012 & 99.95\% &  Alfa Aesar \\
\ce{Molybdenum}& 00932 & I07S024 & 99.9\% &  Alfa Aesar\\
\bottomrule
\end{tabular}
\end{table}

Silicon substrates was first cleaned according to the procedure in Sec.~\ref{ch2sub} on page~\pageref{ch2sub}. To apply the catalysts, 54 $\mu$L 10 mM \ce{NaOH} (or \ce{KI}, \ce{Na2CO3}) was drop-cast onto clean substrates and then air dried in a chemical fume hood. Other alkali ions-containing substrates, such as glass (Fisher Scientific, microscope slide, 12-549) and indium tin oxide (ITO) coated glass (Delta Technologies, 25\si{\ohm}), were cleaned by the same routine except the absence of plasma cleaning and subsequent aqueous solution dipping. Mica was cleaved right before growth without other treatment. 
\begin{table}[htb]
\centering
\caption{Physical constants of reactants }\label{tb:mothermo}
\begin{tabular}{lccr}
\toprule
Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & Reference\\
\midrule
\ce{NaOH}        & 318 & 1388 & \cite{crc1977}  \\
\ce{NaI}         & 651 & 1300 & \cite{crc1977}    \\
\ce{KI}          & 681 & 1330 & \cite{crc1977}   \\
\ce{Na2CO3}      & 851 & Not determined & \cite{crc1977}    \\
\ce{Na2MoO4}     & 687 & Not available & \cite{crc1977}   \\
\ce{MoO3}    & 795 & 1155 & \cite{crc1977}   \\
\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
\bottomrule
\end{tabular}
\end{table}
In a typical synthesis run (Fig.~\ref{fig:mooxgrowth}), about 2 g molybdenum powders were loaded into the uniform heating zone and the sealed chamber was first pumped down to 10 mTorr. 
% cvd layout
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp_MoO3.jpg}
\caption[CVD growth setup of \ce{MoO3}]{CVD growth setup of \ce{MoO3}. The triangular labels $\blacktriangledown$ were measured points at ambient environment. The nominal substrates temperature were estimated from interpolation data.}
\label{fig:mooxgrowth}
\end{figure}
Then oxygen flow varying between 0.1 sccm to 10 sccm (standard cubic centimeter per minute) was admitted from upstream inlet. With 10 sccm UHP Ar as carrier gas, the overall pressure reached about 200 mTorr. The heating temperature was ramped up to 800 \si{\degreeCelsius} in 30 min and lasted for 15 to 120 min. Then the heating power was turned off and the chamber was allowed to naturally cool down to room temperature. The substrate was placed in downstream location where the temperature was about 350 to 650 \si{\degreeCelsius} according to open air temperature profile. Non-catalytic growth shares the same procedure except the NaOH treatment on Si substrates.

@@

\subsection{Non-catalytic Growth}\label{sec:nonsi}

For \ce{MoO3} non-catalytic growth, this study observed the typical micro-flakes morphologies as shown in Fig.~\ref{fig:mosisem}. Most flakes exhibit rectangular shape, with average thickness of one micron, standard deviation $\sigma_D=0.34 \mu$m.
% sem in (31210-31510) batches
\begin{figure}[htb]
\centering
\subfloat[]{\label{fig:mosem1}\includegraphics[width=0.4\textwidth]{mosemsi_a}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:mosem2}\includegraphics[width=0.4\textwidth]{mosemsi_b}}
\caption[Representative morphologies of \ce{MoO3} on Si]{Representative morphologies of \ce{MoO3} on Si: (a) low magnification and (b) high magnification SEM images of representative depositions of \ce{MoO3} on Si for non-catalytic growth.}
\label{fig:mosisem}
\end{figure}

@@

\textsuperscript{\emph{a}} R chain mode;
\end{table}

@@

Previous study in our group has found that \ce{MoO3} deposition on ITO glass exhibits new morphologies that are not observed on Si substrates, yet the mechanism is not well investigated.\cite{predeep2011} Based on the \gls{vls} process, it is known that a eutectic state is the key to promote preferred growth direction. A list of composition difference between glass and Si substrate shows the extra elements of Na, K, Ca, \emph{etc}. Since the concentration of Na is highest among these extra elements, it is most likely to induce the new morphology growth. A literature search indeed shows that there exists \ce{Na2MoO4}-\ce{MoO3} phase diagram as shown in Fig.~\ref{fig:ch4pd}.\cite{Hoermann1929} Notice that the phases of the Na-Mo-O system can be written as \ce{Na2O.nMoO3}, where n = 1, 2, 3, and 4.

@@

Based on this phase diagram, the physical constants of reactants in Table~\ref{tb:mothermo}, and the growth conditions adopted in this study, it is predicted that the overall reactions occur in the following sequences. First, Mo powder is oxidized and \ce{MoO3} vapor is produced and transported to downstream by Ar carrier gas. Then NaOH reacts with incoming \ce{MoO3} according to Formula~\ref{eq:pd}. 
\begin{subequations}\label{eq:pd}
\begin{align}
\cee{NaOH(l) + MoO3(g) &\rightarrow Na2MoO4 + H2O(g)\\
Na2MoO4 + nMoO3   &\rightarrow Na2O.(n + 1)MoO3}
\end{align}
\end{subequations}
The melting point of \ce{Na2MoO4} is 687 \si{\degreeCelsius}. Based on the open air temperature profile (Fig.~\ref{fig:mooxgrowth}), the substrate is located in temperature zone between 650 and 350 \si{\degreeCelsius}. The actual temperature distribution during growth is different from ambient measurement due to the pressure change and thermal conduction along the Si substrate. It is difficult to acquire the accurate values along the substrate; however, by considering the flow rate, the actual temperature will be higher than predicted by open air measurement.\cite{Subannajui2010} The melting of \ce{Na2MoO4} is highly possible when taking into account of its size as well.\cite{Bruggemann1997} The continuous supply of \ce{MoO3} growth species will push the phase evolution towards high \ce{MoO3} molar ratio end, with $n$ in \ce{Na2O.nMoO3} increasing from 1 to 4. Each site of \ce{Na2MoO4} will continue absorb incoming \ce{MoO3}, forming a swelling particle. \ce{MoO3} will precipitate from these seeds when a critical supersaturation concentration is reached, which is about 75\% in unit of mole according to Fig.~\ref{fig:ch4pd}. This ratio considerably exceeds that of the usual metal catalyst scenario. This high solubility accounts for several observations in current experiments: the dimensions of individual deposit is much larger than that of initial particle, the concentration of sodium in final products is extremely low. Based on this aforementioned analysis, the author proposed following hypothesis:
%theorem environment

\emph{The reaction on NaOH-Si substrate follow the phase diagram, and \ce{Na2Mo4O13} serves as the catalyst promoting various 1D \ce{MoO3} growth.}

In a typical 2 h growth, the \ce{MoO3} weight increase is about 20 mg, which is about $1.4\times 10^{-4}$ mol. This amount far exceeds the applied NaOH of $5\times 10^{-7}$ mol used in the procedure of Sec.~\ref{sec:grow} on page~\pageref{sec:grow}. To capture the early stage growth, the supply of \ce{MoO3} must be reduced in a controlled way. This can be accomplished by tuning two factors: oxygen flow rate and growth time. In this thesis, two series of controlled growth were used to probe the evolution of \ce{MoO3} deposition on NaOH-Si substrate. The first series regulated \ce{O2} flow at 0.1, 1, 3, and 10 sccm with fixed growth time of 15 min. The second series controls growth time at 15, 30, 60, and 90 min with fixed \ce{O2} flow of 10 sccm. Two series share one common growth of 10 sccm \ce{O2} for 15 min.

The oxygen regulated growths were characterized using SEM, EDX and Raman, as shown in Fig.~\ref{fig:ch4oxy}. When \ce{O2} flow was $\leq 1$ sccm, the deposition show micron size plate growth (Fig.~\ref{fig:ch4oxy}a and d). As oxygen flow becomes higher, the deposition amount increased dramatically, with a morphology of 1D forked plate decorated by triangular shape particles.
% sem
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{MoO3_EDX_Raman}
\caption[Evolution of the early stage for catalyst-assisted \ce{MoO3} growth]{Evolution of the early stage for catalyst-assisted \ce{MoO3} growth: SEM images, micro-Raman spectra, and EDX spectra of the specimens grown for 15 min with different \ce{O2} flows of (a-c) 0.1 sccm, (d-f) 1 sccm, (g-i) 3 sccm, and (j-l) 10 sccm. }
\label{fig:ch4oxy}
\end{figure}

Micro-Raman scattering was used to probe the phase change during the oxygen regulated growth. The Raman spectra of sodium molybdates is featured with multiple strong peaks located between 800 and 1000 \si{cm^{-1}}, which we refer as high-frequency region hereafter. \ce{MoO3} phase shows two peaks in this region with the strongest one at about 820 \si{cm^{-1}}; \ce{Na2Mo2O7} phase exhibits four peaks in this region with the strongest one moving to 937 \si{cm^{-1}}, whereas \ce{Na2Mo4O13} phase shows even more peaks in high-frequency region, with a doublet at 962 and 970 \si{cm^{-1}}, respectively.\cite{Schofield2005,Saraiva2011} As predicted by the phase diagram (Fig.~\ref{fig:ch4pd}), Raman spectra identified \ce{Na2Mo2O7} phase in the 0.1 sccm growth (Fig.~\ref{fig:ch4oxy}b), and \ce{Na2Mo4O13} phase on the particles in the rest three growths (Fig.~\ref{fig:ch4oxy}e, h, and k). This observation supports the previous hypothesis about the reaction sequence on NaOH-Si substrate (Formula~\ref{eq:pd}). Element analysis performed on the Raman sites also confirm the presence of Na, Mo and O in particles growth, and only Mo and O in the plate growth (Fig.~\ref{fig:ch4oxy}c, f, i, and l). It is worth noting that the absence of Na signal in the forked \ce{MoO3} plate indicates the doping level would be lower than the detection limit of 0.01 wt.\% if the Na doping ever occurs. It should be pointed out the existence of \ce{Na2Mo3O10} phase is in doubt so far, and no Raman fingerprint is reported.\cite{Fomichev1992} Table~\ref{tb:moo3ram} compared the Raman spectra of sodium molybdates and \ce{MoO3} between present work and literature reports.
% moo3ram
\begin{landscape}
\begin{table}[htb]
\centering
\caption{Comparison of Raman shift (\si{cm^{-1}}) of sodium molybdates and molybdenum oxide}\label{tb:moo3ram}
\begin{tabular}{lllllllll}
\toprule
        & \ce{Na2Mo2O7}    &    &    & \ce{Na2Mo2O7}    &       &       & \ce{MoO3}   &    \\
\midrule
\cite{Saraiva2011} & \cite{Fomichev1992} & this work& \cite{Fomichev1992} & \cite{Schofield2005} & this work   & \cite{Eda1992} & \cite{Siciliano2009}   &  this work   \\
\midrule
 939    & 939/935 & 937         &        & 995    & 995         & 995    & 996       & 996   \\
 921    & 920/918 & 919         & 970    & 971    & 970         & 819    & 819       & 820   \\
 873    & 875/869 & 873         & 960    & 963    & 962         & 666    & 666       & 667   \\
 833    & 836/828 & 833         & 940    &        &             & 471    & 473       &       \\
 821    & 818/815 &             & 925    &        & 926         & 378    & 378       & 380   \\
 768    & 774/765 &             & 910    & 918    & 915         & 366    & 365       & 364   \\
 741    & 741/739 &             & 895    & 899    & 898         & 338    & 337       & 338   \\
 524    & 526/525 &             & 870    &        &             & 291    & 291       & 291   \\
 467    & 464/460 &             & 835    & 841    & 841         & 283    & 283       & 284   \\
 413    & 411/411 &             &        & 820    & 819         & 246    & 244       & 245   \\
 369    & 369/368 & 366         & 745    &        &             & 217    & 218       & 216   \\
 339    & 340/336 & 340         & 650    & 666    &             & 197    & 197       & 199   \\
 295    & 296/294 &             &        & 620    & 619         & 159    & 158       & 156   \\
 249    & 245/245 &             & 438    &        &             & 129    & 129       &       \\
 226    & 228/227 & 226         &        &        & 417         & 117    & 117       &       \\
        & 215/215 &             & 405    &        &             & 100    & 98        &       \\
 200    & 199/199 & 198         &        & 396    & 393         & 84     & 84        &       \\
 176    &         &             & 382    & 381    &             &        &           &       \\
 137    & 140/138 &             &        & 368    &             &        &           &       \\
 120    & 120/120 &             & 348    &        &             &        &           &       \\
 84     & 84/84   &             & 335    & 339    & 336         &        &           &       \\
        & 45/44   &             & 320    & 320    & 318         &        &           &       \\
 36     &         &             & 295    & 293    &             &        &           &       \\
        &         &             & 272    &        & 267         &        &           &       \\
        &         &             & 255    &        &             &        &           &       \\
        &         &             &        & 246    &             &        &           &       \\
        &         &             & 220    & 225    & 224         &        &           &       \\
        &         &             &        & 202    &             &        &           &       \\
        &         &             &        & 159    & 155         &        &           &       \\
\bottomrule
\end{tabular}
\end{landscape}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{MoO3_SFig_EDX}
\caption[SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures]{SEM images and EDS spectra identifying the location, morphology, and composition of the catalyst particles on the nanobelt structures: (a-b) a catalyst particle (I) in the middle of a nanobelt (II), (c-d) two catalyst particles (I and II) leading the growth of two perpendicular nanobelts.}
\label{fig:ch4edx1}
\end{figure}

@@

\begin{enumerate}
\item When no Mo powder is used, NaOH still holds onto substrate with some locations exhibiting etching.
\item When no Mo powder is used while growth is performed in an old tube or oxygen flow is limited to a extreme small value, circular particle-like solid were found and Mo, Na and O were detected, suggesting the existence of VLS mechanism. Using Mo coated substrate and subsequent NaOH treatment, similar particles formation was repeated. No discernible XRD pattern emerged, illustrating the amorphous nature of liquid catalyst.
\item 1 min growth shows plates in high temperature end and irregular shapes in low temperature end.
\item 15 min growth shows \ce{MoO3} plates parallel to substrate, with some belts emerging and growing out of the substrate plane. This is presumably due to the growth direction mismatch between different plates. Morphology will also depend on local NaOH concentration. NaOH trace mark turns into connected plates at the original locations, showing the high concentration mediated the morphology evolution. The possible catalyst solid was sitting on the top of plate layer. Also some belt-like growth is visible on reaction chamber walls, suggesting the evaporation and transport of \ce{Na_xMoO3} vapor phase;
\item 30 min growth: belts growth begin (500 microns long, grow rate is estimated to be 0.5 $\mu$ m/s), tower structures show up as well, but much less than belt. Two kinds of belts found, tapering and non-tapering. The former one seems to have particles mostly associated with sidewalls of the top part.
\item In reduced time or less oxygen supply growth, Na-containing site was found located onto the sidewall of belts instead of the usual expected tip. XRD pattern indicated the existence of \ce{Na_xMoO3} phase. And \ce{MoO3} XRD pattern is dominated by (0k0) peaks, indicating a 2D layer-by-layer growth with lateral rate exceeding that of axial direction.
\item 2 h growth: there are crossed tapering belts at downstream boundary, with more than one particle located along the interface of two perpendicular belts, EDX confirmed high Na content.
\item Using NaOH treated hydrophobic substrates, dense tower array growth was found along the edge areas or molten periphery of particles, where 5 min growth already show the initial stage of tower with diameter about 1 $\mu$ m, which increase to 10 $\mu$ m in prolonged growth.
\end{enumerate}
